\section{Question Valuation}

    \begin{enumerate}
        \item PostgreSQL \\  Store questions, model answers, rubrics, student submissions, scores, and audit logs in a relational DB.
        \item OpenAI (with Structured Outputs) \\ Evaluate each answer against the rubric and return structured JSON per criterion (score, justification, evidence span).
        \item Claude  \\ Act as a second‑opinion grader or judge model for high‑stakes or borderline cases.
        \item Grading rubric engine  \\ Custom JSON/YAML stored in DB. Hold question‑specific rubrics; the app reads these and injects them into LLM prompts as clear scoring criteria.
        \item Evaluation logic \\ Application code (Python/JS). Compute final marks from per‑criterion scores, enforce caps, apply penalties, and flag borderline answers.
        \item Prompt testing(Promptfoo) \\ Load grading rubrics and answer pairs, systematically test grading prompts, and compare rubric‑based scores across LLM versions.
        \item Observability \\ Log prompts, rubrics, scores, and reasoning; track LLM‑as‑a‑judge metrics and flag unreliable or inconsistent grading.
        \item Quality benchmarking \\ Ragas or custom benchmark set. Run offline experiments to compare grading behavior, rubric design, and LLM versions on labeled teacher‑scored answers.
        \item Human review UI \\ Let teachers review auto‑graded answers, override scores, add notes, and calibrate the system against human markers.
        \item Student result UI \\ Show students their scores, rubric‑based feedback, and quoted evidence from their answers.
        \item Evaluation method \\ LLM‑as‑a‑judge pattern. Use LLMs to score answers per rubric criterion, then combine numeric scores externally and log decision trails.
    \end{enumerate}